---
title: "class9 Pipelines and Automation"
author: "Emily West"
date: "11/7/2017"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

GUEST Lecturer: Shaun Jackman
The dark side of automating: yak shaving
If you do something more than 3 times, it is worth automating
Why split up analysis into multiple files?
  integrating someone into the project becomes more challenging
  certain steps take a long time- those should be seperated 
  think "manageable chunks"
  
Each stage of a pipeline
  define stage
  CLEARLY define input and output (name, type of input/output)
  do NOT modify inputs, "idempotent", always write out to a different file
    independent steps mean you can rerun pipelines downstream
    chunks of analysis can be assigned to different people
  pipelines can be visual!
  
Why automate a pipeline?
  reproducability
  recreate results deleted by fat fingas
  to rerun pipeline with updated software
  to run the same piepline on a new dataset
  
Tools
R
shell
makefile

make
  A pipeline is a dependency graphy
  each vertex is a stage
  each edge is a dependency between stages
  dependency graphs can be non-linear, making automation so crucial
  make is visual and programmatic
  a make file 

shell
  gives one order
  
Syntax of a makefile
shell:
  set -euc
  dot -Tpng -o figure.png figure.gv
  Rscript
makefile  
all:
  dot -Tpng -o figure.png figure.gv
  Rscript -e 'knitr::knit("article.Rmd")'
  pandoc -s -o article.html article.md
  
What if you're changing the article between steps?
all: article.html
  article.html: article.Rmd
    dot -Tpng -o figure.png figure.gv
    Rscript -e 'knitr::knit("article.Rmd")'
    pandoc -s -o article.html article.md
  article.html:articl.Rmd is a dependency - you can add dependency to 
    
    
  article.html: article.Rmd
  figure.png: figure.gv
    dot -Tpng -o figure.png figure.gv
    Rscript -e 'knitr::knit("article.Rmd")'
    pandoc -s -o article.html article.md
sjackman.ca/makefile-slides
    
```{r}

```

```{r}

```

