---
title: "Intro to prr"
author: "Emily West"
date: "10/31/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
##vectors
#an atomic vector is composed of elements all of the same type (within that vector) (pearl necklace )
(v_log<-c(TRUE, FALSE, FALSE, TRUE)) #all logical
(v_int<-1:4) #all integers, 
#each elements has a length of 1

(v_double <- 1:4*1.2) #parentheses short hand the print function
typeof(v_double)
(v_char<-letters[1:4])
typeof(v_char)
##Index with a logical vector
v_char[c(FALSE, FALSE,TRUE,TRUE)] #index using logical vector, return only the elements that are true- basically a filter

v_char[v_log]

#index by position
v_double[2:3]
v_char[-4] #negative to drop out an element

v_int[1]

typeof(v_int[1])
v_doub_copy <- v_double
str(v_doub_copy) #numeric vector
#It is really easy to mess up a vector by coercing it to a different type

v_doub_copy[3]<-"uhoh"
str(v_doub_copy) #now a character string! no longer an atomic vector
```

#Lists
```{r}
(x<-list(1:3,c("four","five"))) # a list does not care that the elements are of a different type
(y<- list(logical = TRUE, integer = 41, double = 4*3.2, character = "character"))
(z<-list(letters[26:22], transcendental = c(pi, exp(1)), f= function(x) x^2))# you can even have a function in a list

```

#CHALLENGE: in list y pull out the second and third elements, in list z pull out all the transcendental numbers

```{r}
y[2:3]
z[2]
z["transcendental"] #but this returns a list, not an atomic vector! We have no "reached" into the list
z$transcendental #index by the name of the element
typeof(z["transcendental"])
typeof(z[["transcendental"]])
typeof(z$transcendental) #$ is like double bracket indexing
#the pepper shaker analogy of indexing into a list which are highly nested

y[["double"]]
y["double"]
y$double
```

prrr
```{r}
##consider how to square the integers 1 through n 
n<-5
# you could do this by hand, or you could use a for loop

res<- rep(NA_integer_, n) #kills the vector so you have all NAs first
  for(i in seq_len(n)){
    res[i]<- i^2
    }
  
res

(1:n)^2 #square all the integers 1 to n

exp(v_double)

(l_doub<- as.list(v_double)) #force the atomic vector into a list

exp(l_doub) #non numeric argument
#THis is where map functions in purr become really useful!

library(purrr)

map_dbl(l_doub,exp) #even though l_doub is a non-numeric list
#map function is similar to lapply
#map_ (x, f, ...) - x = argument, f = funtion, ...= we'll get to this later
#map_dbl says: take ldoub and exponentiate it
#maps over all of the elements
#map returns type list, map_ returns the typr designated after the "_"

library(stringr)

str(fruit)

#use a map function and a stringer function to split all the fruit that have two words in them
?split()

map_chr(.x=fruit,.f= str_split, " ") #does not like character

fruit %>% 
  map(str_split, " ")

fruit %>% 
  map_chr(str_to_upper)

```

Get advanced: Joey Berhardt github
```{r}
#install.packages("repurrrsive")
library(repurrrsive)
#install.packages("listviewer")
library(listviewer)
#install.packages("jsonlit")
library(jsonlite)
library(dplyr)
library(tibble)
library(purrr)
```

```{r}
str(gh_users)
head(gh_users)

jsonedit(gh_users) #a fun interactive way to view data tht is nested

gh_users[[1]]
map(gh_users,"login")#index by name
gh_users %>%map(18) #index by position

#what if we want to get out multiple values
map(gh_users,'[', c("login","name")) 
# [ can be used to extract elements of a list!

map(gh_users, magrittr, extract, c("login", "name"))

```

##Guilio takes over
```{r}
rm(list=ls(all=TRUE))
list(letters)
#nested lists make things ugly
library(tidyverse)
library(purrr)
library(repurrrsive)
#library(listviewer)
#jasonedit(gh_users)

```

```{r}
#An ugly nested dataframe: gh_repos
#str(gh_repos) - hard to access elements directly
data("gh_repos") #allows you to explore data in superficial way through the global environment- similare to View(), it is important to always explore your dataset before doing anything else
gh_repos[[1]]
View(gh_users)
```

#Warmup and refresh challenge
extract information from lists
```{r}
#purr allows you to more easily access data in nested lists
#mapping functions are one of purr's greatest tools
gh_repos[[2]][[2]][["name"]]

gh_repos %>% 
  map_chr(c(2,2)) #look at the second element of the second element of the first list 

gh_repos %>% 
  map_chr(list(2,"name")) #this would give you just the name on the second repo

getNamespaceExports("purrr") #what are the purrr functions availabile - by exploring your data 

gh_repos %>% map_chr(c(1,2))
gh_repos %>% map_chr(list(1,"name")) #use list() instead of c() to return non-character data

```

#Challenge: extract information from lists:owner ID of fourth repo for each user
```{r}
gh_repos %>% 
  map_int(list(4,"owner","id")) #each comma represents next step...map_XXX XXX indicates the type of element you are selecting

#dataframes are preferred, gh_repos is a nested list

```

```{r}
library(tibble)
enframe() #search for a variable name and translate it to a variable in a dataframe
u_id <- gh_repos %>% 
  map_int(list(1,"owner","id"))
str(gh_repos, max.level = 1) #stop at the first level of the data, note there are no names for any of the elements

#we want to set names 
gh_repos_named <-gh_repos %>% 
  set_names(u_id)

str(gh_repos_named, max.level = 1) #now lists are named based on user ID

#get a dataframe for gh_repos
gh_repos_df<- gh_repos_named %>% enframe("user_id", "repository_stuff") #enframe, give column names

gh_repos_df
enframe()
```

#Challenges continue: create an enframed df of repos with rownames being their login
```{r}
#MODIFY existing code
login<-gh_repos %>% 
  map_chr(list(1,"owner","login"))

gh_repos_named2 <-gh_repos %>% 
  set_names(login)

gh_repos_df2<- gh_repos_named2 %>% enframe("user_login", "repository_stuff")
gh_repos_df2
View(gh_repos_df2)
```

```{r}
gh_repos_df2  %>% filter(user_login %in% c("masalmon", "leeper")) %>% mutate(number_of_repositories = length(repository_stuff))

gh_repos_df2  %>% filter(user_login %in% c("masalmon", "leeper")) %>% mutate(number_of_repositories = map_l(repository_stuff))#??????
```

```{r}
got_chars

map(got_chars, "name")

aliases_named<-set_names(map(got_chars, "aliases"), map(got_chars, "name")) #make a list with all the names and aliases from got dataset

View(aliases_named)
length(aliases_named)#number of elements in the list, but does not go deeper into nested list
map_int(aliases_named, length) #for each element how many occurrences

collapse_by_comma<- function(x){
  paste(x, collapse = ", ")
}

collapse_by_comma(c("first string,", "second string"))

map(aliases_named, collapse_by_comma)
map(aliases_named, function(x) paste(x, collapse= ", ")) #define function inside the map function
map(aliases_named, paste, collapse = ", ")
map(aliases_named, ~paste(.x, collapse = ", ")) # ~ special character, .x 

```

