---
title: "Web scraping"
author: "Emily West"
date: "11/28/2017"
output: html_document
---

#All about webscraping

sometimes data available online is not is an easy to use format


```{r}
library(tidyverse)
library(magrittr)
library(purrr)
library(glue)
library(stringr)
```

```{r}
library(rvest)
library(xml2)
```
we'll start by downloading some lyrics from the internet
navigate to the website of interest, some websites are more amenable to webscraping than others

let's get a list of song titles first
the inforation we want is here:
```{r}
my_url<- "https://www.musixmatch.com/artist/Straight-Line-Stitch"
page_title<-read_html(my_url)
```

what's in "page title"" now?
```{r}
page_title %>% View

```

xml is a glorified list
elements of a document:
<doc> document starts here
  <head>
  </head> head ends here
  <body>
    <div> is simply a section 
  </body> body ends here
</doc> document ends here

what browsers should you use? Not all are created, use firefox developer
this gives you the developer view of the page
control shift c in google chrome also gives you the developer view

command alt k to see developer
select a section within the website
right click on the object> copy> css selector or css path

```{r}
page_title %>% 
  html_nodes(css = ".title") %>% 
  html_text()
```

we don't want just the title, we want the lyrics too

```{r}
SLS_lyrics <- data_frame(Band = "Straight LIne Stitch", Title = page_title %>%
                          html_nodes(css = ".title") %>% 
                          html_text(),
                        Link = glue('https://www.musixmatch.com/lyrics/{Band}/{Title}'))

SLS_lyrics$Link[1] #yikes there is white space!

SLS_lyrics2 <- data_frame(Band = "Straight LIne Stitch", Title = page_title %>%
                          html_nodes(css = ".title") %>% 
                          html_text(),
                        Link = glue('https://www.musixmatch.com/lyrics/{Band}/{Title}') %>% str_replace_all(" ","-"))
SLS_lyrics2$Link[1] #Perf.

```

```{r}
#use magrittr operator instead because we are 
SLS_lyrics2 %<>% 
  mutate(Lyrics = map(Link, read_html))

View(SLS_lyrics2)#not actually the lyrics - an ugly html
```

get lyrics, navigate to lyrics page, what class do you get when you hover over them with the cursor
```{r}
get_lyrics<- function(lyr_link){
  lyr_link %>% 
    read_html() %>% 
    html_nodes(css = ".mxm-lyrics__content") %>% 
    html_text() %>% 
    collapse(sep = "\n") %>% 
    return()
}

```

```{r}
SLS_lyrics2 %<>% 
  mutate(Lyrics = map_chr(Link, get_lyrics))
SLS_lyrics2$Link[1] %>% get_lyrics()
```

CHallenge: repeat code with Angel Haze
```{r}
my_url<- "https://www.musixmatch.com/artist/Angel-Haze"
page_title2<-read_html(my_url)
```

```{r}
page_title2 %>% View

```

```{r}
page_title2 %>% 
  html_nodes(css = ".title") %>% 
  html_text()
```

```{r}
AH_url<-"https://www.musixmatch.com/search/angel%20haze#"
AH_lyrics <- data_frame(Band = "Angel Haze",
                        
                         Title = AH_url %>%
                          read_html() %>%
                           html_nodes(css = ".title") %>%
                           html_text(),
                        
                         Link = AH_url %>%
                          read_html() %>%
                           html_nodes(css = ".title") %>%
                          html_attr("href")
                        )

```

getting lyrics: use a map_XXX from purr to get the lyrics
```{r}
AH_lyrics %<>% 
  mutate(Lyrics = map(Link, read_html))

View(AH_lyrics)#not actually the lyrics - an ugly html
```

```{r}
get_lyrics<- function(lyr_link){
  lyr_link %>% 
    collapse("https://www.musixmatch.com/artist/Angel-Haze")
    read_html() %>% 
    html_nodes(css = ".mxm-lyrics__content") %>% 
    html_text() %>% 
    collapse(sep = "\n") %>% 
    return()
}

AH_lyrics %>% if( get_lyrics())

```

```{r}
AH_lyrics %<>% 
  mutate(Lyrics = map_chr(Link, get_lyrics))
AH_lyrics$Link[1] %>% get_lyrics()
```

```{r}
#"https://www.musixmatch.com/artist/Angel-Haze" %>% read_html() %>% 
  #html_nodes(css= ".title") %>% 
  #html_attr("href")
```

```{r}
get_lyrics_safe<-possibly(get_lyrics, "None available") 
#tries to apply a function, have to give an otherwise argument (NA_character-), possibly is like an if then statement but when it fails you get "none available"
```

###A Tribe Called Red
```{r}
ATCR_url<-"https://www.musixmatch.com/artist/A-Tribe-Called-Red#"
ATCR_lyrics <- data_frame (Band = "A tribe called red",
                           Title = ATCR_url %>% 
                             read_html() %>% 
                             html_nodes(css = ".title") %>% 
                             html_text(), 
                           Link = ATCR_url %>% 
                             read_html() %>% html_nodes(css = ."title") %>% html_attr("href"),
Lyrics = map(Link, get_lyrics_safe) %>% unnest()
  
```

BONUS SENTIMENT ANALYSIS
```{r}
install.packages("tidytext")
library(tidytext)

```

API
```{r}
thor<-GET("http://www.omdbapi.com/?t=thor&y=2017&apikey=c0f86156")
thor_content<-content(thor)
View(thor_content)
```

```{r}
get_movie_TV<- function (title, year){
  query_string<- glue("http://www.omdbapi.com/?t={title}&y={year}&apikey=c0f86156")
movie_result<-GET(query_string)
movie_content<- content(movie_result)
return(movie_content)
}
```

```{r}
babe<- get_movie_TV("babe", "1995")

matrix<- get_movie_TV("matrix", "1998")
View(matrix) #this is ugly, empty spaces are bad!
```

