---
title: "class07 writing functions in R"
author: "Emily West"
date: "10/26/2017"
output: github_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Functions in R!
```{r}
#functions takes in an object and returns an output
#some functions are not found in base R
#reduces the amount time spent writing code
#if you use a chunk more than once in your code you should write a function
```

```{r}
library(gapminder)
str(gapminder)
```

there is no built in function to calculate max and min
```{r}
min(gapminder$lifeExp)
max(gapminder$lifeExp)
range(gapminder$lifeExp)
```

```{r}
max(gapminder$lifeExp)-min(gapminder$lifeExp)
with(gapminder, max(lifeExp)-min(lifeExp))
range(gapminder$lifeExp)[2] - range(gapminder$lifeExp)[1]
with(gapminder, range(lifeExp)[2] - range(lifeExp)[1])
diff(range(gapminder$lifeExp))
```

```{r}
max_minus_min <- function(x) max(x) - min(x)
max_minus_min(gapminder$lifeExp)

max_minus_min(1:10)
max_minus_min(runif(1000))
```

```{r}
max_minus_min(gapminder$gdpPercap)
max_minus_min(gapminder$pop)
```

#Try to break the function
```{r}
max_minus_min(gapminder) #dataframe
max_minus_min(gapminder$country) #character
max_minus_min("eggplants are purpler") #String
```
when the function should break
```{r}
#why isn't this throwing an error? R will try to compute as possible, R will take Trues and Falses as 1s and 0s
max_minus_min(gapminder[c('lifeExp', 'gdpPercap', 'pop')]) #string these vectors together and comput max and min on these
max_minus_min(c(TRUE, TRUE, FALSE, TRUE, TRUE))
```

stopifnot
```{r}
#solution to code running when it shoudn't
mmm<-function(x){
stopifnot(is.numeric(x))
max(x)-min(x)
}

mmm(gapminder)
```

#better to use if then stop
```{r}
mmm2 <- function(x) {
  if(!is.numeric(x)) {
    stop('I am so sorry, but this function only works for numeric input!\n',
         'You have provided an object of class: ', class(x)[1])
  }
  max(x) - min(x)
}
mmm2(gapminder) #tells you there is an error, where the error is and possibly how to fix it
```

Challenge
```{r}
#1. create a new function that takes a number and returns the remainder after dividing by 10:
15%%10 #the %% give remainder after division
mod_ten1<- function(x){
  x%%10
  }
#2. Add if then stop statement into function that returns error message if the wrong input is added
mod_ten<- function(x){
  if(!is.numeric(x)){stop("I am so sorry, but this function only works for numeric input!/n'. 'You have provided an object of class'. class(x)[1]")}
  x%%10
  }
#curly braces for if statement if you have more than one line for if statement
mod_ten(gapminder)
```

#generalize function to other quantiles
```{r}
#median = 0.5 quantile
#1st quartile = 0.25 quantile
#3rd quartile = 0.75 quantile

quantile(gapminder$lifeExp)
quantile(gapminder$lifeExp, probs = 0.5)
median(gapminder$lifeExp)
quantile(gapminder$lifeExp, probs = c(0.25, 0.75))
boxplot(gapminder$lifeExp, plot = FALSE)$stats
#write a code that takes the difference between two quantiles
the_probs <- c(0.25, 0.75)
the_quantiles <- quantile(gapminder$lifeExp, probs = the_probs)
max(the_quantiles) - min(the_quantiles)

#this funtion takes in two arguments: x and probs
qdiff1 <- function(x, probs) {
  stopifnot(is.numeric(x))
  the_quantiles <- quantile(x = x, probs = probs)
  max(the_quantiles) - min(the_quantiles)
}

qdiff1(gapminder$lifeExp, probs = c(0.25, 0.75))
```

#Make useful parameter names, what the heck do zeus and hera mean?? think about the parameters the 
```{r}
qdiff2 <- function(zeus, hera) {
  stopifnot(is.numeric(zeus))
  the_quantiles <- quantile(x = zeus, probs = hera)
  return(max(the_quantiles) - min(the_quantiles))
}
qdiff2(zeus = gapminder$lifeExp, hera = 0:1)
```

#return() explicit funtion to deliver an output at any point 
```{r}
qdiff3 <- function(my_x, my_probs) {
 stopifnot(is.numeric(my_x))
  the_quantiles <- quantile(x = my_x, probs = my_probs)
  return(max(the_quantiles) - min(the_quantiles))
}
qdiff3(my_x = gapminder$lifeExp, my_probs = 0:1)


qdiff4 <- function(x, probs = c(0, 1)) {
  stopifnot(is.numeric(x))
  the_quantiles <- quantile(x, probs)
  return(max(the_quantiles) - min(the_quantiles))
}
```

#Problem 2
```{r}
mod_x<-function(value, divisor){
  value%%divisor
}
mod_x(15,6)

#set the default parameter value of divisor to be 10
mod_x10<-function(value, divisor = 10){
  int<-value%/%divisor
  mod<-value%%divisor
  #when you have multiple outputs you should make the output a list
  output<-list(quotient-int, remainder-mod)
  return(output)
}
mod_x10(16)

#add a stopifnot() statement into function that returns informative error message if the divisor is not an integer

mod_x2<-function(value, divisor){
  stopifnot(is.integer(divisor))
  value%%divisor
}
mod_x2(22, 5.2)

```

```{r}
z<-gapminder$lifeExp
z[3]<- NA
quantile(gapminder$lifeExp)
quantile(z)
quantile(z,na.rm = TRUE) #na.rm defaults are often FALSE
```

```{r}
qdiff5 <- function(x, probs = c(0, 1)) {
  stopifnot(is.numeric(x))
  the_quantiles <- quantile(x, probs, na.rm = TRUE)
  return(max(the_quantiles) - min(the_quantiles))
}
qdiff5(gapminder$lifeExp)
qdiff5(z)
```

# ... argument
```{r}
qdiff7 <- function(x, probs = c(0, 1), na.rm = TRUE, ...) {
  the_quantiles <- quantile(x = x, probs = probs, na.rm = na.rm, ...)
  return(max(the_quantiles) - min(the_quantiles))
}
# but what is the type argument doing?
set.seed(1234)
z <- rnorm(10)
quantile(z, type = 1)

#two different type arguments for quantile computing
quantile(z, type = 4)
all.equal(quantile(z, type = 1), quantile(z, type = 4))
qdiff7(z, probs = c(0.25, 0.75), type = 1)
qdiff7(z, probs = c(0.25, 0.75), type = 4)

#... allows you to pass more information through an argument without throwing an error
```

#formally test your function:
```{r}
library(testthat)

test_that('invalid args are detected', {
  expect_error(qdiff7("eggplants are purple"))
  expect_error(qdiff7(iris))
  })

test_that('NA handling works', {
  expect_error(qdiff7(c(1:5, NA), na.rm = FALSE))
  expect_equal(qdiff7(c(1:5, NA)), 4)
})

qdiff_no_NA <- function(x, probs = c(0, 1)) {
  the_quantiles <- quantile(x = x, probs = probs)
  return(max(the_quantiles) - min(the_quantiles))
}
test_that('NA handling works', {
  expect_that(qdiff_no_NA(c(1:5, NA)), equals(4))
})
?return()
```

