---
title: "hw07, step 2: data wrangling"
author: "Emily West"
date: "11/13/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(forcats)
```

In the previous step I created a hw07_datadownload.Rmd, where the gapminder dataset was downloaded and sent to live in my repo as: gapminder.tsv.
Here, I will read in the data, perform some preliminary analysis and save it as a csv

Read the data in:
```{r}
gap<-read.delim("gapminder.tsv")
str(gap)
```

let's continue as if the data download worked:
```{r}
#Instead of re-writing the file path to where figures should be saved I'll #make use of the paste function. Full disclosure, I did not have this stroke #of genius, my roommate is an R goddess.
plot_loc = "/Users/Adelaide/Desktop/UBC_Work/STAT545/stat547/hw07"
csv_loc <- "/Users/Adelaide/Desktop/UBC_Work/STAT545/stat547/hw07"
```


```{r}
levels(gap$continent)
max(gap$year) #2007
min(gap$year) #1952, 55 years of data
```

```{r fig.height = 6, fig.width = 9}
#Descritptive plots:
#plot life expectancy for asian countries from 1952-2007

asia_data<- gap %>% filter(continent =="Asia")

png(file = paste(plot_loc,"fig_scatter-lifeExp-asia.png",sep=""),width = 600,height = 400)
ggplot(data = asia_data) +
  geom_line(mapping = aes(x = year , y = lifeExp, color = country))+ 
  ylab("life expectancy")
dev.off()

#Interestingly, when you write a figure to file it does not print in the markdown, so here is the lovely graph made in the previous step:
ggplot(data = asia_data) +
  geom_line(mapping = aes(x = year , y = lifeExp, color = country))+ 
  xlab("year")+
  ylab("life expectancy")
```

```{r}
#There is a precipitous drop-off in life expectancy for Cambodia, corresponding with the erruption of the Cambodian civil war. Generally, all other countries seem to be experiencing a steady increase in life expectancy with a few expections that experienced increases in the '70s and 80's with a slight decline in the 1990's.
```

```{r fig.height = 6, fig.width = 9}
#Descritptive plots:
#plot life expectancy for asian countries from 1952-2007

euro_data<- gap %>% filter(continent =="Europe")

png(file = paste(plot_loc,"fig_scatter-lifeExp-euro.png",sep=""),width = 600,height = 400)
ggplot(data = euro_data) +
  geom_line(mapping = aes(x = year , y = lifeExp, color = country))+ 
  ylab("life expectancy")
dev.off()

#Interestingly, when you write a figure to file it does not print in the markdown, so here is the lovely graph made in the previous step:
ggplot(data = euro_data) +
  geom_line(mapping = aes(x = year , y = lifeExp, color = country))+ 
  xlab("year")+
  ylab("life expectancy")

#For the other 3 continents:
ams_data<- gap %>% filter(continent =="Americas")
oc_data<- gap %>% filter(continent =="Oceania")
afr_data<- gap %>% filter(continent =="Africa")
```

1. Reorder each continent based on life expectancy:
```{r}
str(euro_data)
eu_oa<-euro_data[order(euro_data$lifeExp),]
head(eu_oa)
as_oa<-asia_data[order(asia_data$lifeExp),]
ams_oa<-euro_data[order(ams_data$lifeExp),]
oc_oa<-euro_data[order(oc_data$lifeExp),]
afr_oa<-euro_data[order(afr_data$lifeExp),]
#or use arrange to get descending order:
euro_ord<-arrange(euro_data, desc(euro_data$lifeExp))
head(eu_od)
asia_ord<-arrange(asia_data, desc(asia_data$lifeExp))
ams_ord<-arrange(ams_data, desc(ams_data$lifeExp))
oceania_ord<-arrange(oc_data, desc(oc_data$lifeExp))
afr_ord<-arrange(afr_data, desc(afr_data$lifeExp))
```

2. Save ordered continents to file

```{r}
?write.csv()
write.csv(asia_ord, file = paste(csv_loc,"asia_ordered.csv", sep=""))
write.csv(euro_ord, file = paste(csv_loc,"europe_ordered.csv", sep=""))
write.csv(ams_ord, file = paste(csv_loc,"americas_ordered.csv", sep=""))
write.csv(oceania_ord, file = paste(csv_loc,"oceania_ordered.csv", sep=""))
write.csv(afr_ord, file = paste(csv_loc,"africa_ordered.csv", sep=""))
```



```{r}
#Reorder continent by lifeExp, the default summarizing function is median(), I chose min
gap_ord<- fct_reorder(gap$continent, gap$lifeExp, min)
gap_ord %>% levels() %>% head()
View(gap_ord)
View(min_cont)
min_cont <-gap %>% group_by(continent) %>% summarize(min_life=min(lifeExp))
min_contord<- fct_reorder(min_cont$continent, min_cont$min_life, min, .desc= TRUE)
str(min_cont)

gap_ord<-gap %>% select(continent, country, lifeExp, year)%>% mutate (continent = fct_reorder(continent, lifeExp, min)) 
levels(gap_ord$continent)

View(gap_ord)
gap_arr<- gap_ord%>% arrange(year, lifeExp)
View(gap_arr)

png(file = paste(plot_loc,"fig_bar-lifeExp-continent.png",sep=""),width = 600,height = 400)
ggplot(min_cont, aes(fct_reorder(continent, min_life), min_life))+
  geom_bar(stat = "Identity")+
  xlab("continent")+
  ylab("minimum life expectancy")
dev.off()

ggplot(gap_ord, aes(fct_reorder(gap_ord$continent, gap_ord$lifeExp), gap_ord$lifeExp))+
  geom_bar(stat = "Identity")+
  xlab("continent")+
  ylab("minimum life expectancy")
dev.off()

#sort the full dataset by country, then by lifeExp
gap_sort<-gap %>% arrange(country, desc(lifeExp))
View(gap_sort)
```

